---
title: "30-feature-engineering"
output: html_notebook
---

# Adding features

## New feature 1: Standardize relative to department

First, I add the standardized feature relative to department. 

The standardized job satisfaction level and score of last evaluation may have impact on employee's leave. Why might standardize be informative? Imagine the job satisfaction level is 0.6, we have no idea whether it's good or not. If the average job satisfaction level is 0.5, then 0.6 is good. If the average job satisfaction level is 0.7, then 0.6 is bad. Standardizing by department rescales a number relative to an employee's department, where 0 indicates the employee's job satisfaction was average for the department, 1 indicates it is one standard deviation above, -1 indicates it is one standard deviation below.

Job satisfaction level and score of last evaluation may vary in different departments, so it's necessary to divide them by department. Standardize measures relative to an employee's department.

```{r, standardize_relative_department}
standardize_relative_department <- function(df, vars) {
  df %>% 
    group_by(department) %>% 
    mutate_at(vars, list(std_dep = scale)) %>% 
    ungroup()
}
```


## New feature 2: Overwork

8 working hours per workday and 5 workdays per week is the normal working scheme. The normal monthly working hours is 40 times 52 then divide 12, which is around 173. Therefore, the employee is overworked if his or her monthly working hours is over 173. 

I add the overwork feature to check whether the employee is overworked or not. I think overwork should have impact on employee's leave.

```{r, check_overwork}
check_overwork <- function(df, var) {
  df %>% 
     mutate(overwork = case_when({{var}} <= 173 ~ FALSE,
                                 {{var}} > 173 ~ TRUE))
}
```


## New feature 3: Average number of project participated per year

I think average number of project participated per year is more meaningful than the total number of project participated for the predicative model.

Therefore, I plan to add a new feature to show average number of project participated per year, it is equal to number of project participated divide year spend in the company (number_project / time_spend_company). 

Function name: average_number_project_per_year
New feature: avg_num_proj_per_year
Column used: number_project, time_spend_company


## New feature 4: Difference between job satisfaction level and score of last evaluation:

I think the difference between job satisfaction level and score of last evaluation is meaningful. Define the difference to be job satisfaction level minus score of last evaluation (satisfaction_level - last_evaluation). This diffenrence measures the cognitive difference between the employee's own satisfaction on the company's job and company's job evaluation on the employee.

Therefore, I plan to add a new feature to show the difference between job satisfaction level and score of last evaluation. 

Function name: get_difference
New feature: diff_btw_satisfaction_evaluation
Column used: satisfaction_level, last_evaluation



# Test new features

## Test new feature 1

Belowe I test whether there are any outliers over 3 standard deviation from the average. As a good standardized new feature, it should not contain any outlier over 3 standard deviation from the average. 

```{r, check_outlier}
hr_analytics %>% 
  standardize_relative_department(c("satisfaction_level", "last_evaluation")) %>% 
  select(contains("std_dep")) %>% 
  assert(within_bounds(-3,3), c("satisfaction_level_std_dep", "last_evaluation_std_dep"))
```

The test above shows that both the new standardized job statisfaction level relative to department and standardized score of last evaluation relative to department are with in 3 standard deviation from the average. 

## Test new feature 2

Below I test whether the overwork only includes True and False.

```{r, test_logical}
hr_analytics %>% 
  check_overwork(monthly_hours) %>% 
  assert(in_set(c(TRUE, FALSE)), overwork)
```

The test above shows that overwork only includes True and False.

## Test new feature 3

Property: Average number of project participated per year should be between 0 and 7 (minimum of number_project) inclusively. 

Function may be used for assert: within_bounds()


## Test new feature 4

Property: Difference between job satisfaction level and score of last evluation should between -1 and 1 (inclusively).

Function may be used for assert: within_bounds()



