---
title: "40-modeling"
output: html_notebook
---

# Prepare data for modeling

A new data frame after feature engineering with new features is generated by applying the fuctions created in 30-feature-engineering. A new csv file is also write for adding into the pipeline.

```{r, apply_feature_functions}
hr_analytics_fe_csv <- "hr_analytics_fe.csv"

hr_analytics_fe <- hr_analytics %>% 
  standardize_relative_department(c("satisfaction_level", "last_evaluation")) %>% 
  check_overwork(monthly_hours) %>% 
  # average_number_project_per_year %>% 
  # get_difference %>% 
  select(contains("std_dep"), overwork, left, everything()) %>% 
  write_csv(hr_analytics_fe_csv)

head(hr_analytics_fe)
```

Then I select the columns used for modeling by deleting the needless columns.

```{r, select_cloumns_for_modeling}
hr_analytics_modeling <- hr_analytics_fe %>% 
  select(everything(), -satisfaction_level, -last_evaluation, -number_project, -monthly_hours, -time_spend_company, -department, -salary)

head(hr_analytics_modeling)
```


# Test new data frame

Here I check the new data frame, whether their are any missing value for all the variables. And I also check the properties of new features.

```{r, test_new_dataframe}
hr_analytics_modeling %>% 
  assert(not_na, everything()) %>% 
  assert(within_bounds(-3,3), satisfaction_level_std_dep, last_evaluation_std_dep) %>% 
  assert(in_set(c(TRUE, FALSE)), overwork)
```

The test above shows the new data frame for modeling is as expected. 



